\sysfull

### 2017-11-15 paper/paging.tex
review of paging section

\paragraph{Dirty victim page.} If a task modified any byte in the victim page (i.e.,  using \texttt{WVAR}), then the page is dirty. Before swapping in the accessed page, \sys must first preserve the updated values in the dirty page so that they can eventually be committed back to their locations in memory when the task ends. To preserve dirty values, \sys copies the victim page to its dedicated memory region called \texttt{pagesTemp}, which is acts as a double buffer for each page of protected memory. Dirty pages copied into {\tt pagesTemp} during a task remain there until the task completes, at which point \sys commits the modified pages from {\tt pagesTemp} back to memory (Lines 2--3).

\paragraph{Dirty accessed page.} If an accessed page is modified, \sys should swap it into the page buffer from its location in {\tt pagesTemp}, rather than swapping it in from its original location in memory. As Algorithm~\ref{algo:pagefault} shows in Line 4, \sys checks if the requested page was previously modified by the executing task. To track whether a page is modified, \sys stores a dirty bit with the page that is set when a task modifies the page. If an accessed page's dirty bit is set, the page must be swapped in from \texttt{pagesTemp} rather than its original memory location (Line 5), furnishing the task with the page's modified values. If the accessed page is not dirty, \sys swaps it in from its original location in memory (Line 7). \sys uses DMA block copies for all page swapping operations, leveraging the efficiency of hardware support.

>>>>

\textbf{Dirty Victim Page.} If a task modified any byte in the victim page (i.e.,  using \texttt{WVAR}), then the page is dirty. Before swapping in the accessed page, \sys must first preserve the updated values in the dirty page so that they can eventually be committed back to their locations in memory when the task ends. To preserve dirty values, \sys copies the victim page to its dedicated memory region called \texttt{pagesTemp}, which is acts as a double buffer for each page of protected memory. Dirty pages copied into {\tt pagesTemp} during a task remain there until the task completes, at which point \sys commits the modified pages from {\tt pagesTemp} back to memory (Lines 2--3).

\textbf{Dirty Accessed Page.} If an accessed page is modified, \sys should swap it into the page buffer from its location in {\tt pagesTemp}, rather than swapping it in from its original location in memory. As Algorithm~\ref{algo:pagefault} shows in Line 4, \sys checks if the requested page was previously modified by the executing task. To track whether a page is modified, \sys stores a dirty bit with the page that is set when a task modifies the page. If an accessed page's dirty bit is set, the page must be swapped in from \texttt{pagesTemp} rather than its original memory location (Line 5), furnishing the task with the page's modified values. If the accessed page is not dirty, \sys swaps it in from its original location in memory (Line 7). \sys uses DMA block copies for all page swapping operations, leveraging the efficiency of hardware support.
